%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps Engineer \& Tech Lead} % Job title
    {Sonrisa Informatikai Kft. (Open Minds Hungary Kft.)} % Organization
    {Budapest, Hungary} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead and empower a dynamic team of 5 professionals, driving innovation and maintaining active involvement in coding and technical execution. Orchestrated 500+ production application/infrastructure deployments for the Client's production environment with impeccable uptime.}
        \item {Assume on-call responsibilities encompassing incident response and meticulous postmortem documentation.}
        \item {While embracing infrastructure as code practices using Terraform an Ansible, I contribute to the CI/CD Team, spearheading the creation of a Jenkins environment with on-demand agents and implementing a comprehensive shared library for enhanced code cleanliness and efficiency.}
        \item {Engage in a wide range of activities beyond client work, including conducting technical interviews, delivering university lectures, mentoring aspiring professionals, and facilitating interactive coding dojos.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Sonrisa Informatikai Kft. (Open Minds Hungary Kft.)} % Organization
    {Pécs, Hungary} % Location
    {Mar. 2016 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated excellence in implementing Infrastructure as Code (IaC) methodologies using Terraform, while establishing robust CI/CD pipelines leveraging Jenkins, GitLab, and Travis. Successfully deployed virtual machines through Vagrant for multiple clients, ensuring meticulous documentation throughout the process.}
        \item {Successfully maintained on-premises data centers, overseeing backup/restore procedures, automating virtual machine provisioning, and implementing scalable and user-friendly warehouse solutions.}
        \item {Played a pivotal role in the deployment of an in-house forum utilizing Discourse, ensuring its seamless functionality.}
        \item {Made significant contributions to the successful migration of in-house services to AWS, facilitating improved scalability and performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Sonrisa Informatikai Kft. (Open Minds Hungary Kft.)} % Organization
    {Pécs, Hungary} % Location
    {Oct. 2013 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Actively participated in 10+ projects, ranging from greenfield to ongoing initiatives, showcasing versatility and adaptability. Leveraged expertise in front-end development, proficiently utilizing AngularJS and CSS to deliver exceptional user experiences.}
        \item {Gained valuable expertise in back-end development, utilizing Java Spring and Apache Wicket frameworks to architect robust and scalable solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
