%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Role
    {SAFe System Demo} % Event
    {Online} % Location
    {Oct. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Contributed as a key presenter in recurring SAFe framework's System Demo ceremonies, showcasing team achievements through engaging live presentations and self-edited recorded videos with screen sharing and green-screen effects, reaching audiences of 200+ people.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Role
    {Growth Mindset: A Personal Journey} % Event
    {Budapest} % Location
    {May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Participated as a guest speaker in an in-house senior engineer round table discussion, sharing insights on career growth, professional transitions, and overcoming challenges in the field of DevOps.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Guest lecturer} % Role
    {IT Life course} % Event
    {University of Pannonia - Veszprém} % Location
    {Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Conducted an impactful session on goal setting and productivity strategies, equipping students with essential skills to achieve their objectives successfully.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Guest speaker} % Role
    {Sonrisa Days} % Event
    {Zamárdi} % Location
    {Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Delivered a compelling presentation on my experience transitioning to a different site within the company, with the support of professional public speech training, at the highly attended company event, showcasing effective communication skills and adaptability in the role of DevOps.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Guest lecturer} % Role
    {IT Life course} % Event
    {University of Pécs - Pécs} % Location
    {Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Delivered an engaging lecture on effective stress management techniques, empowering students to cultivate resilience and well-being.}
        \item {Conducted an impactful session on goal setting and productivity strategies, equipping students with essential skills to achieve their objectives successfully.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
